---
title: "DV04"
output: html_document
date: "2023-10-03"
---

## Question1

```{r, message = FALSE}
library(tidyverse)

tv_ratings <- read_csv("https://raw.githubusercontent.com/vaiseys/dav-course/main/Data/tv_ratings.csv")

glimpse(tv_ratings)
```

```{r}
tv_long <- tv_ratings %>% 
  group_by(title) %>% 
  summarise(num_seasons = n()) %>% 
  ungroup() %>% 
  left_join(tv_ratings, by = "title") 

tv_long <- tv_long %>% 
  filter(num_seasons >= 5)

tv_long
```

```{r, message = FALSE}
library(ggplot2)
```

```{r}
ggplot(data = tv_long,
       mapping = aes(x = seasonNumber,
                     y = av_rating,
                     group = title,
                     fill = title))+
  geom_line(alpha = .2)
```

## Question2

```{r}
ggplot(data = tv_long,
       mapping = aes(x = seasonNumber,
                     y = av_rating,
                     group = title,
                     fill = title))+
  geom_line(alpha = .2)+
  facet_wrap(~genres) +
  theme_minimal()
```

Lasts longer: Comedy, Crime, Drama; Crime, Drama, Mystery; Drama, Romance. Ratings do change a lot across seasons.

```{r}
genre_plummeted <- tv_long %>%
  filter (genres == "Drama,Family,Fantasy")
genre_plummeted
```

The tv show that plummeted is Are You Afraid of Dark.

## Question3

Let's look at the `genres` that show up in the best rated shows.

First, filter the original data set - `tv_ratings` - so that it only includes rows where the average rating is higher or equal than 9.

```{r}
Best_rated_shows <- tv_ratings %>%
  filter (av_rating >= 9)
ggplot(data = Best_rated_shows,
       mapping = aes(x = genres))+
  geom_bar()+
  coord_flip()
```

This function flipped the x and y axis so that we can read the names of the long genres!

Drama is the genre with the top-rated shows.

## Question 4

```{r}
comedies_dramas <- tv_ratings %>% 
  mutate(is_comedy = if_else(str_detect(genres, "Comedy"), 
                             1, 
                             0)) %>% # If it contains the word comedy then 1, else 0
  filter(is_comedy == 1 | genres == "Drama") %>% # Keep comedies and dramas
  mutate(genres = if_else(genres == "Drama", # Make it so that we only have those two genres
                          "Drama", 
                          "Comedy"))

glimpse(comedies_dramas)
```

```{r}
ggplot(comedies_dramas, aes(x = av_rating, color = genres)) +
  geom_density(alpha = 0.5)

```

Obviously comedy rates higher.

## Question5

```{r}
ggplot(comedies_dramas, aes(x = av_rating, fill = genres)) +
  geom_histogram(binwidth = 0.2, position = "dodge")
```

By histogram I can tell the distribution of the average ratings for each genre.

```{r}
ggplot(comedies_dramas, aes(x = av_rating, color = genres)) +
  geom_freqpoly()
```

By freqpoly function helps to identify trends of the ratings.

All of the three plots could do useful comparisons, while I would prefer freqpoly plot, since it more explicitly shows the trends and differences between to genres. The histogram could do the same thing but personally I think the freqpoly plot is easier to read and have an overall comparison.

## Question6

```{r}
ggplot(data = comedies_dramas,
       mapping = aes(x = av_rating,
                     y = share)) +
  geom_bin_2d()
```

```{r}
ggplot(data = comedies_dramas,
       mapping = aes(x = av_rating,
                     y = share,
                     fill = genres)) +
  geom_point()
```

The 2D bin plot helps to identify regions of the plot where there is a higher concentration of data points, indicating areas where average rating and share tend to cluster together(when av_rating = 8 and share\<=5), comparing to scatter plot. I can see that higher share doesn't necessarily indicate higher av_rating.

```{r}
ggplot(data = comedies_dramas,
       mapping = aes(x = av_rating,
                     y = share,
                     fill = genres)) +
  geom_bin_2d()
```
