---
title: "DV05"
output: html_document
date: "2023-10-05"
---

```{r, message = FALSE}
library(tidyverse)
wncaa <- read_csv("https://raw.githubusercontent.com/vaiseys/dav-course/main/Data/wncaa.csv")

glimpse(wncaa)
```

## Question1

```{r, message = FALSE}
library(dplyr)
library(ggplot2)
```

```{r}
champs <- wncaa %>% 
  filter(tourney_finish == "Champ")|>
  group_by(school) %>%
  summarize(percentage_won = n())
champs
```

```{r}
ggplot(data = champs, 
       mapping = aes(x = reorder(school, percentage_won),
                                     y = percentage_won)) +
  geom_bar(stat = "identity")+
  theme_minimal()+
  coord_flip()
```

UConn and Tennessee won the most games. Many of the schools have the same percentage of winning.

## Question2

```{r}
champ_names <- unique(champs$school)
```

```{r}
winners <- wncaa %>% 
  filter(school %in% champ_names)
```

```{r}
ggplot(data = winners, 
       mapping = aes(x = school, y = seed)) +
  geom_boxplot() +
  coord_flip() +
  theme_minimal()
```

```{r}
ggplot(data = winners, 
       mapping = aes(x = school, y = seed)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.2, size = 2, alpha = 0.5) +
  coord_flip()+
  theme_minimal()
```

```{r}
ggplot(winners,
       aes(x = seed, y = reorder(school, seed))) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(alpha = .3) +
  theme_minimal()
```

UConn and Tennessee's median seed is #1! However the median of the seeds is not exactly ranked by school ranking.

```{r}
ggplot(winners,
       aes(x = seed, y = reorder(school, seed))) +
  geom_violin() +
  geom_jitter(alpha = .3) +
  theme_minimal()
```

The violin plot seems more informative to me because it shows the density across seeds value.

## Question3

```{r}
ggplot(winners,
       aes(x = seed, y = reorder(school, seed))) +
  geom_point() +
  geom_jitter(alpha = .3)  +
  theme_minimal()
```

A scatter plot is worse, it does not provide a summary of the distribution. It only plots individual data points, which could be cluttered as shown.

## Question4

```{r}
winners_mean_sd <- winners |> 
  group_by(school) |> 
  summarize(across(where(is.numeric),
                   list(mean = mean,
                        sd = sd)))
winners_mean_sd
```

```{r}
ggplot(data = winners_mean_sd, 
       mapping = aes(x = reorder(school, reg_percent_mean), 
                     y = reg_percent_mean)) +
  geom_point() +
  coord_flip() +
  labs(
    title = "Average Win Percentage Across Seasons by School",
    x = "School",
    y = "Average Win Percentage"
  ) +
  theme_minimal()
```

UConn has significantly highest average win percentage, while Texas A&M has the lowest.

```{r}
ggplot(data = winners_mean_sd, 
       mapping = aes(x = reorder(school, reg_percent_mean), 
                     y = reg_percent_mean)) +
  geom_pointrange(aes(ymin = reg_percent_mean - reg_percent_sd, ymax = reg_percent_mean + reg_percent_sd)) +
  coord_flip() +
  labs(
    title = "Average Win Percentage Across Seasons by School",
    x = "School",
    y = "Average Win Percentage"
  ) +
  theme_minimal()
```

Texas A&M has the narrowest interval. Having the narrowest intervals for certain schools means that their win percentages are relatively consistent and close to the mean win percentage.

```{r}
ggplot(data = winners_mean_sd, 
       mapping = aes(x = reorder(school, reg_percent_mean), 
                     y = reg_percent_mean)) +
  geom_linerange(aes(ymin = reg_percent_mean - reg_percent_sd, ymax = reg_percent_mean + reg_percent_sd)) +
  coord_flip() +
  labs(
    title = "Average Win Percentage Across Seasons by School",
    x = "School",
    y = "Average Win Percentage"
  ) +
  theme_minimal()
```

I think the point range is more helpful to see where the mean value is.
