---
title: "MD05"
output: html_document
date: "2023-10-12"
---

```{r}
library(tidyverse)

twitch_data <- read_csv("https://raw.githubusercontent.com/vaiseys/dav-course/main/Data/twitchdata-update.csv")

library(janitor)
twitch_data <- clean_names(twitch_data)

colnames(twitch_data)
```

## Question1

```{r}
library(dplyr)

random_streamers <- twitch_data %>% sample_n(5)
random_streamers %>%
select(channel,average_viewers,followers)

random_streamers
```

I notice that streamers with more followers don't usually have more average viewers.

```{r}
library(dplyr)

twitch_data %>%
  select(average_viewers, followers) %>%
  summary()
```

The average viewers among all streamers is 4781, and the average followers is 570054. There is a significant difference between median and mean, which could mean that some streamers have exceptionally high numbers in average viewers and the followers.

```{r}
library(ggplot2)
ggplot(data = twitch_data,
       mapping = aes(x = average_viewers, y = followers))+
  geom_point(alpha = 0.2)
```

Most of the data cluttered together under 25000 average viewers and under 2500000 followers, but still some streamers have significant high values.

```{r}
ggplot(data = twitch_data, mapping = aes(x = average_viewers, y = followers)) +
  geom_point(alpha = 0.2) +
  geom_smooth()+
  scale_x_log10()+
  scale_y_log10()
```

dddd

```{r}
twitch_data <- twitch_data %>% 
  mutate(log_viewers = log10(average_viewers), 
         log_followers = log10(followers))
```

## Question2

Using `lm()` fit a model where you predict the logarithm of average viewers (`log_viewers`) using the logarithm of followes (`log_followers`). Save the results to an object called `fit1`.

```{r}
fit1 <- lm(log_viewers ~ log_followers,
           data = twitch_data)

get_regression_table(fit1)
```

```{r}
library(broom)
tidy(fit1)
```

1% increase in viewers is associated with a 79.9% in followers.

## Question3

```{r}
library(broom)

pred_data <- augment(fit1)

glimpse(pred_data)
```

```{r}
pred_data %>% 
  ggplot(aes(x = log_followers, 
             y = log_viewers)) +
  geom_jitter(alpha = 0.4) + 
  geom_line(aes(x = log_followers, 
                y = .fitted), 
            col = "orange") + 
  theme_minimal() +
  labs(subtitle = "Fitted Model and Raw Data", 
       title = "Followers & Average Viewership", 
       x = "log(followers)", 
       y = "log(viewers)")
```

The orange line captures a general trend and indicates a positive linear relationship between log-transformed followers and log-transformed viewers. The jitter points are from the raw data, indicates variability.

```{r}
pred_data %>%
  ggplot(aes(x = log_followers, y = log_viewers)) +
  geom_line(data = pred_data, 
            mapping = aes(x = log_followers, y = .resid), col = "orange") + 
  theme_minimal()
```

Residuals do happen often in a particular range in the x-axis (from 4.5 to 6.5). It means our model would systematically fail to predict part of our data.

## Question4

```{r}
head(twitch_data)
```

```{r}
twitch_data %>%
  select(average_viewers, language) %>%
  summary() 
table(twitch_data$language)
```

```{r}
ggplot(data = twitch_data,
         mapping = aes(x = reorder(language, average_viewers), 
                       y = average_viewers)) +
  geom_bar(stat = "summary") +
  coord_flip()+
  theme_minimal() +
  labs(
    title = "Average Viewership by Language",
    x = "Language",
    y = "Average Viewers"
  )
```

Surprisingly English only ranked 4th among all the channels of all language. The language with most average viewers is Russian, followed by Spanish and Arabic.

## Question5

```{r}
twitch_data <- twitch_data %>% 
  mutate(language = as.factor(language), 
         language = relevel(language, ref = "English"))
```

```{r}
fit2 <- lm(average_viewers ~ language, 
            data = twitch_data)

get_regression_table(fit2)
```

If the coefficients is positive, it suggests that the streaming language associated with more average viewers compared to English, vice versa. A smaller positive or larger negative coefficient indicates closer to the English average viewers. Only three of the language has positive coefficient and the others are all negative.

## Question6

```{r}
pred_data <- augment(fit2)

residual_plot <- pred_data %>%
  ggplot(aes(x = average_viewers, y = .resid)) +
  geom_point(alpha = 0.4) +
  geom_smooth() +
  scale_x_log10() +
  theme_minimal() +
  labs(subtitle = "Residual Plot", title = "Residuals vs. Average Viewers", x = "Average Viewers", y = "Residuals")

residual_plot
```
